\chapter*{Acknowledgments}
\markright{Acknowledgments}
First and foremost, I would like to thank Prof. Dr. Elke Scheer for making it possible for me to work on this project. I thank her for her trust and the freedom to work with the setups and equipment. Further I thank for the constructive discussions and helpful suggestions.

I thank Prof. Dr Angelo Di Bernardo for his support as my second reviewer, his fruitful suggestions, and his incredible expertise.

I would like to thank Andreas Bloch for his calm, uncomplicated and reflective way of patiently supervising my work. I would also like to thank him for teaching me about sample preparation, the technique for transport measurements and the operation of the HelioxVL setup. 

Furthermore, I would like to thank Sergej Andreev, who introduced me to FMR technique at low temperatures. Likewise for the introduction to the measurement wiring, control and repair of the BlueFors setup.

At this point I would also like to thank Martin Prestel for the introduction for cooling down the BlueFors to base temperature. My thanks also go to Lukas Kammermeier and Roman Hartmann for their help with programming and sample preparation.

I would also like to thank the whole working group for the most inspiring working atmosphere and the great hours spent together at lunch and coffee break. Thank you Guyse!\\
\\
\indent Ich möchte mich bei meinen Kommilitonen und Freunden Jacob, Daniel und Michael, für den Beistand und die vielen gemeinsamen nerdigen Stunden in den letzen Jahren bedanken.

Danki Anki, für deine Hilfe und Unterstützung, auch Abseits dieser Arbeit.

Danke an meine Familie, für diese unglaubliche Chance, die endlose Unterstützung und das tiefe Vertrauen, dass mein Weg der Richige sein wird. Danke euch Dreien!

Danke an alle, die mir eine Fortsetzung meines Weges ermöglichen!

\setcounter{footnote}{0}
% inspirational quote
\vfill\begin{centering}
{\selectfontsize{14pt}\underline{\textbf{The Road not Taken}\footnote{Robert Frost ($^*$1874, $^\dagger$1963)}}}\vspace{0.8cm}\\
...\\
Two roads diverged in a wood, and I--\\
I took the one less traveled by,\\
And that has made all the difference.\\
\end{centering}\vfill